Incremental tactics

### 2012-05-05 doc/papers/LFMTP2012/paper.tex
paper

As is customary, we adopt the Barendregt convention for naming bound
variables, write $A\to B$ for $\prd x A B$ when $\var x\notin \FV{B}$,
$\meta X$ for $\smeta X \msubstnil$, and adopt indifferently list, map
or set notations for $\sigma$ and $\Gamma$. The identity substitution
$\msubstid{\Gamma}$ is a notation for $\{\msubst x {\var x}\ |\ \var x
\in\dom\Gamma\}$.

@@

A \emph{signature} declares object and type constants to be used in
objects. To each object constant we assign an annotation $L$ setting
the slicing behaviour of the constant during type-checking: either
sliceable $\annsliceable$ (each application of this constant will be
cached and given a name), non-sliceable $\annnonsliceable$ (we don't
create a name for applications of this constant), or defined
$\anndefined{T}$ (see \ref{sec:computational-calculus}).
\begin{align*}
  L &\gequal
  \annsliceable \gor
  \annnonsliceable \gor
  \anndefined{T}
  \\
  \Sigma &\gequal
  \gnil \gor
  \gcons \Sigma {\cst c :^L A} \gor
  \gcons \Sigma {\cst a :^L K}
  &\text{Signature}
\end{align*}
We write $\Sigma(\cst c) = A; L$ for $(\cst c :^L A) \in \Sigma$
suggesting the implementation of signatures as maps.

@@

The algorithm is presented in Fig. \ref{fig:typing-algo} as a
syntax-directed inference system. All judgements are of the form $\gjo
U V W$ where $U$ and $V$ are inputs, $V$ is the induction hypothesis
and $W$ the output. They are parameterized by a constant and implicit
signature $\Sigma$, and all premisses are ordered in the algorithmical
order of computation.

@@

@@

  \caption{Typing algorithm for the core calculus}
  \label{fig:typing-algo}
\end{figure*}

@@

Definitional equality judgement between two families $\jea\mr\Gamma A
{A'}$ is used by these typing rules. This equivalence is usually
defined to be just $\alpha$-equivalence since our objects are in
$\beta\eta$-canonical form. Here, objects can contain metavariables
defined in $\mr$, so we shall thread it. Moreover, we will see in next
section how defined constants compute and thus influence definitional
equality. Definitional equality is defined later in

>>>>

As is customary, we adopt the Barendregt convention for naming bound
variables, write $A\to A'$ for $\prd x A A'$ when $\var x\notin \FV{A'}$,
$\meta X$ for $\smeta X \msubstnil$, and adopt indifferently list, map
or set notations for $\sigma$ and $\Gamma$. The identity substitution
$\msubstid{\Gamma}$ is a notation for $\{\msubst x {\var x}\ |\ \var x
\in\dom\Gamma\}$.

@@

A \emph{signature} declares object and type constants to be used in
objects. To each object constant we assign an annotation $L$ setting
the slicing behaviour of the constant during type-checking: either
sliceable $\annsliceable$ (each application of this constant will be
cached and given a name), non-sliceable $\annnonsliceable$ (we don't
create a name for applications of this constant), or defined
$\anndefined{T}$ (see \ref{sec:computational-calculus}).
\begin{align*}
  L &\gequal
  \annsliceable \gor
  \annnonsliceable \gor
  \anndefined{T}
  \\
  \Sigma &\gequal
  \gnil \gor
  \gcons \Sigma {\cst c :^L A} \gor
  \gcons \Sigma {\cst a : K}
  &\text{Signature}
\end{align*}
We write $\Sigma(\cst c) = A; L$ for $(\cst c :^L A) \in \Sigma$
suggesting the implementation of signatures as maps.

@@

The algorithm is presented in Fig. \ref{fig:obj-typing} as a
syntax-directed inference system. All judgements are of the form $\gjo
U V W$ where $U$ and $V$ are inputs, $V$ is the induction hypothesis
and $W$ the output. They are parameterized by a constant and implicit
signature $\Sigma$, and all premisses are ordered in the algorithmical
order of computation.

@@

  \fbox{$\jl\mr\Gamma A S \mmr{S'}{A'}$}
  \qquad
  {Spine typing}

@@

  \caption{Typing algorithm for objects}
  \label{fig:obj-typing}
\end{figure*}

@@

Definitional equality judgement between two families $\jea\mr\Gamma A
{A'}$ is used by these typing rules. This equivalence is usually
defined to be just $\alpha$-equivalence since objects are in
$\beta\eta$-canonical form. Here, objects can contain metavariables
defined in $\mr$, so we shall thread it. Moreover, we will see in the
next section how defined constants compute and thus influence
definitional equality. Definitional equality is defined later in
\ref{fig:def-eq}.

Signatures themselves need to be checked. We present the checking
algorithm in Fig. \ref{fig:sign-typing}.

\begin{figure*}
  \fbox{$\jsig\mr\Sigma\mmr{\Sigma'}$}
  \qquad
  {Signature}

  \begin{mathpar}
    \infer{ }{
      \jsig\mr\gnil\mr\gnil
    }

    \infer{
      \jsig\mr\Sigma\mmr{\Sigma'}
      \and
      \jfam\mmr\gnil {\!_{\Sigma'} A}\mmmr {A'}
    }{
      \jsig\mr{\gcons\Sigma{{\cst c :^L A}}}\mmmr{\gcons{\Sigma'}{{\cst c :^L A'}}}
    }

    \infer{
      \jsig\mmr\Sigma\mmmr{\Sigma'}
      \and
      \jkind\mr\gnil {\!_{\Sigma'} K}\mmr {K'}
    }{
      \jsig\mr{\gcons\Sigma{{\cst a : K}}}\mmmr{\gcons{\Sigma'}{{\cst a : K'}}}
    }
  \end{mathpar}

  \fbox{$\jfam\mr\Gamma A \mmr {A'}$}
  \qquad
  {Family}

    \infer{
      \jfam\mr\Gamma {A_1} \mmr {A_1'}
      \and
      \jfam\mmr{\gcons\Gamma{\tp {\var x} {A_1'}}} {A_2} \mmmr {A_2'}
    }{
      \jfam\mr\Gamma {\prd x {A_1} {A_2}} \mmmr {\prd x {A_1'} {A_2'}}
    }

    \infer{
      \Sigma(a) = K
      % TODO
    }{
      \jfam\mr\Gamma {\app{\cst a} S} \mmr {\app{\cst a} {S'}}
    }

  \fbox{$\jkind\mr\Gamma K \mmr {K'}$}
  \qquad
  {Kind}

  \caption{Typing algorithm for signatures}
  \label{fig:sign-typing}
\end{figure*}
